Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-10 paper/BayesianLISTA.tex
figure captions fixed

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
\caption{Predictive accuracy on different number of layers (for neural networks) or iterations (for baselines) on the synthetic data}
\label{fig:number_of_layers_synthetic}
\end{figure}

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
\caption{Predictive performance on different size of observations on the synthetic data}
\label{fig:unsersampling_synthetic}
\end{figure}

@@

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
\label{fig:mnist_100}
\end{figure}

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
\caption{Predictive performance on number of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
\label{fig:mnist_250}
\end{figure}

@@

The performance on the actively updated train data is compared with the performance on the randomly updated train data, when at every iteration the random element is moved from pool set to train set. Both algorithms of new data sampling were run with $20$ random seeds and their performance was averaged. Figure \ref{fig:active_learning_mnist} demonstrates their performance.The uncertainty sampling has some advantage compared to random sampling, this means that the posterior variance is adequately estimated.
\begin{figure}[t]
\centering
\subfloat[\textsc{nmse}]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/nmse_validation}}%
\subfloat[F measure]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/f_measure_validation}}
\caption{Performance in the active learning experiment on the \textsc{mnist} data. }
\label{fig:active_learning_mnist}
\end{figure}

>>>>

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/nmse_validation}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_number_of_layers/f_measure_validation}}
\caption{Predictive accuracy for different numbers of layers (for neural networks) or iterations (for baselines) on the synthetic data}
\label{fig:number_of_layers_synthetic}
\end{figure}

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/nmse_validation}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/synthetic_undersampling/f_measure_validation}}
\caption{Predictive performance for different sizes of observations on the synthetic data}
\label{fig:unsersampling_synthetic}
\end{figure}

@@

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_non_normalised_f_measure_valid}}
\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with dictionary size $K = 100$}
\label{fig:mnist_100}
\end{figure}

\begin{figure}[t]
\centering
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_nmse_valid}}
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_non_normalised_f_measure_valid}}
\caption{Predictive performance for different numbers of iterations on the \textsc{mnist} data with dictionary size $K = 250$}
\label{fig:mnist_250}
\end{figure}

@@

The performance on the actively updated train data is compared with the performance on the randomly updated train data, when at every iteration the random element is moved from pool set to train set. Both algorithms of new data sampling were run with $20$ random seeds and their performance was averaged. Figure \ref{fig:active_learning_mnist} demonstrates their performance.The uncertainty sampling has some advantage compared to random sampling, this means that the posterior variance is adequately estimated.
\begin{figure}[t]
\centering
\subfloat[\textsc{nmse}]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/nmse_validation}}%
\subfloat[F measure]{\includegraphics[width=0.5\columnwidth]{graphics/active_mnist/f_measure_validation}}
\caption{Performance for the active learning experiment on the \textsc{mnist} data. }
\label{fig:active_learning_mnist}
\end{figure}
